Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-14 Paper/ms.tex
Captions

\begin{figure}
\includegraphics[scale=0.45]{Figures/nu_oph_periods.eps}
\caption{The posterior distribution for the orbital periods in the $\nu$ Oph
system.\label{fig:nu_oph_periods}}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.45]{Figures/gliese581_periods.eps}
\caption{The posterior distribution for the orbital periods in the Gliese 581
system.\label{fig:gliese581_periods}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.45]{Figures/nu_oph_periods.eps}
\caption{The posterior distribution for the orbital periods in the $\nu$ Oph
system. The two dashed vertical lines are the commonly accepted periods
of $530.3$ and $3190$ days.\label{fig:nu_oph_periods}}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.45]{Figures/gliese581_periods.eps}
\caption{The posterior distribution for the orbital periods in the Gliese 581
system. The solid lines are Gliese 581 b and c, the dashed lines are
``planets'' d and e, and the dotted lines are f and g.
\label{fig:gliese581_periods}}
\end{figure}
